---
title: "Exam 2"
author: "Westley Cook"
date: "3/28/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# standard first load

library(tidyverse)

# installing this package and loading the library as instructed worked fine for
# me! Was worried after others had problems, but no problems here

library(Ecdat)

# loading to use rep_sample_n()

library(infer)

# loading to make a nice table in 2b

library(gt)

```

## Question 1: Wrangling Ecdat

### 1A)

```{r question_1a, echo=FALSE}

# This r chunk finds the percentage of men in the sample with wives who are
# neither covered by their husband's health insurance nor have health insurance
# from their own work, then formats that percentage and assigns it to an object
# to insert in the mad lib.

# I filter using hhi == "no" and whi == "no", but could just have easily
# filtered both by using != "yes" to get the same result. I then count the
# number of rows to get the number of men in the sample who meet these
# specifications, and divide that by the number of rows in HI to get the
# percentage of all men in the sample, assigning it to an object because I was
# unable to pipe the resulting decimal value directly into the round() function

pct_no_hhi_whi <- HI %>% 
  filter(hhi == "no",
         whi == "no") %>% 
  count() %>% 
  pull(n) / nrow(HI)

# Formatting the decimal value from above by multiplying by 100, then rounding
# to 2 digits as specified

answer_1a <- round(pct_no_hhi_whi * 100, digits = 2)

```

**`r answer_1a`** percent of men in the sample are married to women who are neither covered by their husband’s insurance nor have health insurance from their own work.

### 1B)

```{r question_1b, echo=FALSE}

# This r chunk sets the seed to 1 (to standardize randomness for easy grading)
# and creates a 90% confidence interval for the mean income of married black men
# using 1,000 bootstrapped resamples. It then assigns the nicely-formatted lower and
# upper bounds each to an object to be inserted in the mad lib.

set.seed(1)

# Subsetting the data for black men; could have used subset() command instead,
# but this seemed quick and easy

HI_black <- HI %>% 
  filter(race == "black")

# Using the subset data and rep_sample_n() to take 1,000 bootstrapped resamples.
# Grouping by replicate and summarizing to find the mean for each sample, then
# pulling the average income for each sample and using quantile() to find the
# upper bound of the 90% confidence interval (at the 95th percentile of the
# distribution of bootstrapped resamples). Assigning the result to an object
# called upper.

upper <- HI_black %>% 
  rep_sample_n(size = 1241, reps = 1000, replace = TRUE) %>% 
  group_by(replicate) %>% 
  summarize(avg_income = mean(husby)) %>% 
  pull(avg_income) %>% 
  quantile(.95)

# Resetting the seed; this is necessary to maintain standardization, since I
# re-make the distribution of bootstrapped resamples before taking the lower
# bound

set.seed(1)

# Copied and pasted code from the upper bound calculation, changing just the
# quantile argument to take the 5th percentile of the distribution of
# bootstrapped resamples rather than the 95th. Assigning the result to a new
# object called lower

lower <- HI_black %>% 
  rep_sample_n(size = 1241, reps = 1000, replace = TRUE) %>% 
  group_by(replicate) %>% 
  summarize(avg_income = mean(husby)) %>% 
  pull(avg_income) %>% 
  quantile(.05)

# Formatting upper, then lower, by multiplying by 1,000 (the unit for the income
# variable), displaying it in regular (non-scientific) notation using format =
# "f", adding a comma, and rounding to 0 digits after the decimal point.
# Assigning each value to a new object, which I insert in the mad lib

upper_bound <- formatC(upper * 1000, format = "f", big.mark = ",", digits = 0)
lower_bound <- formatC(lower * 1000, format = "f", big.mark = ",", digits = 0)

```

The upper bound of a 90% confidence interval for the mean income of married black men is
**`r upper_bound`** and the lower bound of this interval is **`r lower_bound`**.

### 1C)

**Bayesian Interpretation** (statement about *probability*):

We can be 90% confident that the true mean income of married black men in the United States falls between the upper and lower bounds of this interval; in other words, there is a 90% chance that the interval captures the true population mean.

**Frequentist Interpretation** (statement about *the process of creating the interval*):

90% of the time we create an interval using the bootstrap method we used here, the interval will contain the true mean income of married black men in the US. (We hope it did this time, but we're not sure.)

### 1D)

```{r question_1d, echo=FALSE}

# This r chunk modifies the HI data by adding a column showing the total number
# of kids per respondent (a factor with values 0, 1, 2, and "3 or more"). It
# then makes a density plot of hours worked grouped by number of kids

# This is a two-step mutation. First, I add together the columns for kids under
# 6 and kids 6-18, producing n_kids to show the total number of kids per
# respondent. Then, I create n_kids_fct, first using case_when to convert values
# of n_kids >= 3 to the string "3 or more" and setting all other values to
# characters (e.g. 2 becomes "2"), and then converting all those character
# strings to factors

HI_new <- HI %>% 
  mutate(n_kids = kidslt6 + kids618) %>% 
  mutate(n_kids_fct = as.factor(
                        case_when(
                          n_kids >= 3 ~ "3 or more",
                          TRUE ~ as.character(n_kids))))

# Making the plot was straightforward after the data was properly wrangled.
# Hours worked (whrswk) goes on the x axis, and n_kids_fct is the fill. I use
# alpha = 0.4, theme_classic(), and scale_fill_viridis_d() as instructed, adding
# the name argument to give a title to the legend. Finally, I add a title, axis
# labels, and caption to the plot, using the exact text from the model plot I'm
# replicating

HI_new %>% 
  ggplot(aes(whrswk, fill = n_kids_fct)) +
  geom_density(alpha = 0.4) +
  theme_classic() +
  scale_fill_viridis_d(name = "Kids") +
  labs(title = "Hours Wife Works A Week",
       x = "Hours Worked",
       y = "Density",
       caption = "Data from Olson (1998)")

```

## Question 2: my_cold_call()

### 2A)

```{r question_2a_setup, echo=FALSE}

# This r chunk creates the my_cold_call() function

# Defining function and setting the students.csv file as the default value for
# file_name. I first assign rand_n, a random integer between 1 and 7 inclusive;
# this will be the number of students sampled by my_cold_call(). I then assign
# the students tibble from file_name, specifying column type to get rid of a
# message otherwise generated by read_csv(). Finally, I use sample_n to sample
# (with replacement) rand_n students from the students tibble, and pull() the
# values to return a character vector

my_cold_call <- function(file_name = "raw-data/students.csv"){
  rand_n <- sample(1:7, 1)
  students <- read_csv(file_name,
                       col_types = cols(name = col_character()))
  
  sample_n(students, rand_n, replace = TRUE) %>% 
    pull()
}

# Below, I put my_cold_call() in its own r chunk with echo=TRUE so it will show
# up in the HTML without any comments or other clutter in the code box. I set
# the seed to 10 just to demonstrate that the result of my sampling is the same
# as that in the question prompt

```

```{r question_2a, echo=TRUE}

set.seed(10)
my_cold_call()

```

### 2B)

```{r question_2b, echo=FALSE}

# This r chunk creates the "days" tibble and shows the first four rows of it in
# a gt table

# Creating the days tibble by assigning the values 1:36 to the day column and
# using map(rep()) to pass the file name through the my_cold_call() function 36
# times to create the list column of names for the students column

days <- tibble(day = 1:36,
               students = map(rep("raw-data/students.csv", 36), my_cold_call))

# Slicing the first four rows of days and passing it through gt() to produce a
# nice table. then adding title, subtitle, and nice column labels

days %>% 
  slice(1:4) %>% 
  gt() %>% 
  tab_header(title = "Cold Calls",
             subtitle = "First Four Days of Class") %>% 
  cols_label(day = "Day",
             students = "Students")

```



